Quality Definitions of Qualities

### 2019-11-20 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Add correctness, reliability, usability and verifiability from Ghezzi1991 text book

@@

@@

@@

>>>>

\begin{defn}
``A program is functionally correct if it behaves according to its stated
functional specifications'' \citep{ghezzi1991fundamentals}.
\end{defn}

@@

\begin{defn}
``Informally, software is reliable if the user can depend on it''
\citep{ghezzi1991fundamentals}.
\end{defn}

@@

\begin{defn}
``A software is usable - or user fridendly - if its human users find it easy to
use'' \citep{ghezzi1991fundamentals}.
\end{defn}

@@

\begin{defn}
A software system is verifiable if its properties can be verified easily
\citep{ghezzi1991fundamentals}.
\end{defn}
